---
title: "HW1"
output: github_document
author: "Amy Yeung (ay2543)"
date: "2022-09-22"
---

```{r, message=F}
library(tidyverse)
```


# Problem 1

## Load `penguins` dataset

```{r,  message=F}
data("penguins", package = "palmerpenguins")
```

## Describe the `penguins` dataset


### Variables and data
```{r}
colnames(penguins)
skimr::skim(penguins)
```
There are 8 variables in the `penguins` dataset:

* species (factor variable)
* island (factor variable)
* bill_length_mm (character variable)
* bill_depth_mm (character variable)
* flipper_length_mm (character variable)
* body_mass_g (character variable)
* sex (factor variable)
* year (character variable)

### Size of dataset
```{r}
nrow(penguins)
ncol(penguins)
```
There are 344 observations and 8 variables.

### Mean flipper length
```{r}
mean(penguins$flipper_length_mm, na.rm=T)
```
The mean flipper length is 200.9152 mm.

### Scatterplot of flipper_length_mm vs bill_length_mm

```{r}
  ggplot(penguins, 
  aes(x = bill_length_mm, 
      y = flipper_length_mm,
      color = species)) +
geom_point()


```

### Save scatterplot
```{r}
ggsave("problem1_scatter.pdf", device = "pdf")
```


# Problem 2

```{r}
df = tibble(
  norm_dist = rnorm(n = 10),
  positive_dist = norm_dist > 0,
  
)
```







