---
title: "HW1"
output: github_document
author: "Amy Yeung (ay2543)"
date: "2022-09-22"
---

```{r, message=F}
library(tidyverse)
```


# Problem 1

## Load `penguins` dataset

```{r,  message=F}
data("penguins", package = "palmerpenguins")
```

## Describe the `penguins` dataset


### Variables and data
```{r}
colnames(penguins)
head(penguins)
```
There are 8 variables in the `penguins` dataset:

* species (factor variable)
* island (factor variable)
* bill_length_mm (double variable)
* bill_depth_mm (double variable)
* flipper_length_mm (integer variable)
* body_mass_g (integer variable)
* sex (factor variable)
* year (integer variable)

### Size of dataset
```{r}
nrow(penguins)
ncol(penguins)
```
There are 344 observations and 8 variables.

### Mean flipper length
```{r}
penguins %>% 
  pull(flipper_length_mm) %>% 
  mean(na.rm = TRUE)
```
The mean flipper length is 200.9152 mm.

### Scatterplot of flipper_length_mm vs bill_length_mm

```{r}
  ggplot(penguins, 
  aes(x = bill_length_mm, 
      y = flipper_length_mm,
      color = species)) +
geom_point()


```

### Save scatterplot
```{r}
ggsave("problem1_scatter.pdf", device = "pdf")
```


# Problem 2

## Create dataframe
```{r}
df = tibble(
  norm_dist = rnorm(n = 10),
  positive_dist = norm_dist > 0,
  chr = letters[1:10],
  fac = factor(c("low", "middle", "high", "low", "middle", "high", "low", "middle", "high", "high"))
)

# Preview df
head(df)
```

## Taking means

```{r}
# 1. norm_dist
df %>% 
  pull(norm_dist) %>% 
  mean()
```
The mean of `norm_dist` is `r mean(df$norm_dist)`.

```{r}
# 2. positive_dist
df %>% 
  pull(positive_dist) %>% 
  mean()
```

The mean of `positive_dist` is `r mean(df$positive_dist)`.

```{r}
# 3. chr
df %>% 
  pull(chr) %>% 
  mean()
```
A mean cannot be obtained for `chr` as it is a chararcter variable.

```{r}
# 4. fac
df %>% 
  pull(fac) %>% 
  mean()
```

A mean cannot be obtained for `fac`.

## Factor conversion

```{r, eval=FALSE}
df %>% 
  pull(norm_dist) %>% 
  as.numeric()

df %>% 
  pull(positive_dist) %>% 
  as.numeric()

df %>% 
  pull(chr) %>% 
  as.numeric()

df %>% 
  pull(fac) %>% 
  as.numeric()
```

* It worked for `norm_dist` as it was originally a numeric vector.
* It worked for `positive_dist` and converted the True/False values into 1/0 binary values
* It didn't work for `chr` and everything became NA
* It worked for `fac` and converted each level into 1/2/3


